Creating Supplementary Table of all Performances

### 2019-04-18 Scripts/creating_supplementary_table_of_all_performances.Rmd
editted script for supp table 3

all_rfperfs_df$CellLine <- c(rep("GM12878",19*48),rep("K562",19*48))
all_rfperfs_df$Resolution <- rep(c(rep("10 kb", 19*3),rep("25 kb", 19*3),rep("50 kb", 19*3),rep("100 kb", 19*3)),8)
all_rfperfs_df$Resampling <- rep(c(rep("None",19*12),rep("ROS",19*12),rep("RUS",19*12),rep("SMOTE",19*12)), 2)
all_rfperfs_df$PredictorType <- rep(c("OC", "OP", "Distance"),19*32)

>>>>

all_rfperfs_df$CellLine <- c(rep("GM12878",19*48),rep("K562",19*48))
all_rfperfs_df$Resolution <- rep(c(rep("10 kb", 19*3),rep("25 kb", 19*3),rep("50 kb", 19*3),rep("100 kb", 19*3)),8)
all_rfperfs_df$Resampling <- rep(c(rep("None",19*12),rep("ROS",19*12),rep("RUS",19*12),rep("SMOTE",19*12)), 2)
all_rfperfs_df$PredictorType <- rep(c(rep("OC",19),
                                      rep("OP", 19),
                                      rep("Distance",19)),4*8)
